---
title: "County Health Rankings Dashboard"
autor: "Francine Graham"
date: last-modified
format: 
  dashboard:
    nav-buttons: [github]
    github: https://github.com/fvg57/dashboard
theme: default
fig-width: 10
fig-asp: 0.3
params: 
  year: "2024"
  threshold_diff: 0.02
editor_options: 
  chunk_output_type: console
---

```{r install_packages}
#install.packages('ggsignif')
#install.packages('ggpmisc')
```

```{r, message=FALSE, warning=FALSE}
#library(nhanesA) #this does not work
#library(patchwork)
library(mosaic)
library(sessioninfo)
library(janitor)
library(naniar)
library(DT)
library(ggpmisc)
library(datawizard)
library(knitr)
library(bootstrap)
library(scales)
library(ggsignif)
library(easystats)
library(dplyr)
library(boot)
library(tidyverse)
theme_set(theme_light())
knitr::opts_chunk$set(comment=NA)
```

```{r ingest_data, message=FALSE}
data_url <-
  "https://www.countyhealthrankings.org/sites/default/files/media/document/analytic_data2024.csv"
chr_2024_raw<-read_csv(data_url,skip=1,guess_max=4000,show_col_types=FALSE) |>
  select(fipscode,county,state,county_clustered,year,ends_with("rawvalue")) |>
  filter(county_clustered==1)
```

```{r selection}
# Data are from County Health Rankings used in Project A, primarily because I know that this data should work

# State Selection
# I will be focusing exclusively on the Midwest states that border the Great Lakes (OH,IN,IL,MN,WI,MI)
chr_2024_state<-chr_2024_raw|>
    filter(state=="OH"|state=="WI"|state=="IN"|state=="IL"|state=="MI"|state=="MN")

# Variable Selection
# I will use state as a categorical variable across analyses and compare means of several variables
# for further analysis, I will "bin" certain demographics, to have those function as categorical variables (eg: counties that are mostly male (<50% female) and counties that are mostly female (>50% female))

# select state, % female, rural, voter turnout, and population
chr_2024_filtered<-chr_2024_state|>
  select(fipscode,county,state,starts_with("v057"),
  starts_with("v177"),starts_with("v051"),starts_with("v058"))
```

```{r clean_data}
# rename variables
chr_2024<-chr_2024_filtered|>
  rename(female_raw=v057_rawvalue,rural_raw=v058_rawvalue,
  voter_turnout=v177_rawvalue,county_population=v051_rawvalue)
num_obs<-nrow(chr_2024)
num_il<-nrow(chr_2024|>filter(state=="IL"))
num_in<-nrow(chr_2024|>filter(state=="IN"))
num_mi<-nrow(chr_2024|>filter(state=="MI"))
num_mn<-nrow(chr_2024|>filter(state=="MN"))
num_oh<-nrow(chr_2024|>filter(state=="OH"))
num_wi<-nrow(chr_2024|>filter(state=="WI"))

# bin counties
chr_2024<-chr_2024|>
  mutate(
    gender=case_when(
      female_raw>0.5~"Female",
      female_raw<0.5~"Male"
    ),
    # pick a coefficient that allows a nonzero number of counties in each category
    county_size=case_when(
      county_population>mean(county_population)+0.3*sd(county_population)~"Large",
      county_population<mean(county_population)-0.3*sd(county_population)~"Small",
      TRUE~"Average"
    ),
    urban=case_when(
      rural_raw>0.9~"Rural",
      rural_raw<0.2~"Urban",
      TRUE~"Mixed"
    ),
    female_raw=case_when(female_raw<1.1~female_raw*100,TRUE~female_raw),
    rural_raw=case_when(rural_raw<1.1~rural_raw*100,TRUE~rural_raw),
    voter_turnout=case_when(voter_turnout<1.1~voter_turnout*100,TRUE~voter_turnout)
  )

```

#  {.sidebar}

This dashboard displays statistics from:

|              |                        |
|--------------|------------------------|
| **States**   | IL, IN, MI, MN, OH, WI |
| **Counties** | `{r} num_obs`          |
| **Years**    | CHR: 2024              |
|**Voter Data**| 2016 & 2020            |
| **% Female** | 2022                   |
| **% Rural**  | 2020                   |

------------------------------------------------------------------------

The breakdown of `{r} num_obs` counties across these states is:

|                    |              |
|--------------------|--------------|
| **Illinois (IL)**  | `{r} num_il` |
| **Indiana (IN)**   | `{r} num_in` |
| **Michigan (MI)**  | `{r} num_mi` |
| **Minnesota (MN)** | `{r} num_mn` |
| **Ohio (OH)**      | `{r} num_oh` |
| **Wisconsin (WI)** | `{r} num_wi` |

------------------------------------------------------------------------

::: {.callout-note collapse="true"}
## Disclaimer

Analyses performed are representative of counties rather than individuals, meaning that associations of demographics and predictors are representative of county trends, which may not sufficiently include nuance to draw causal conclusions.

For multiple comparisons, insignificant comparisons are not shown to reduce clutter.
:::

# Overview

```{r}
#| label: all-values
#| results: hide


chr_2024<-chr_2024|>
  mutate(
    votes=floor(voter_turnout/100*county_population),
    rural_voters=floor(voter_turnout/100*county_population*rural_raw/100),
    female_voters=floor(voter_turnout/100*county_population*female_raw/100),
    
)
overall_turnout<-sum(chr_2024$votes)/sum(chr_2024$county_population)

```

## Row {height="20%"}

```{r}
#| content: valuebox
#| title: "Total Population"

list(
  #icon="clipboard2-pulse",
  color="primary",
  value=sum(chr_2024$county_population)
)
```

```{r}
#| content: valuebox
#| title: "Total Voter Turnout"

list(
  #icon="file-medical",
  color="secondary",
  value=label_percent(accuracy=0.1)(overall_turnout)
)
```

```{r}
#| content: valuebox
#| title: "Estimated Rural Voter Turnout"

list(
  #icon="clipboard2-pulse",
  color="green4",
  value=label_percent(accuracy=0.1)(sum(chr_2024$rural_voters)/sum(chr_2024$county_population))
)
```

```{r}
#| content: valuebox
#| title: "Estimated Female Voter Turnout"

list(
  #icon="clipboard2-pulse",
  color="orange",
  value=label_percent(accuracy=0.1)(sum(chr_2024$female_voters)/sum(chr_2024$county_population))
)
```

## Row {height="40%"}

### Column {width="30%"}

```{r}
#| title: State Turnouts

il_chr<-chr_2024|>filter(state=="IL")
in_chr<-chr_2024|>filter(state=="IN")
mi_chr<-chr_2024|>filter(state=="MI")
mn_chr<-chr_2024|>filter(state=="MN")
oh_chr<-chr_2024|>filter(state=="OH")
wi_chr<-chr_2024|>filter(state=="WI")

il_turnout<-sum(il_chr$votes)/sum(il_chr$county_population)
in_turnout<-sum(in_chr$votes)/sum(in_chr$county_population)
mi_turnout<-sum(mi_chr$votes)/sum(mi_chr$county_population)
mn_turnout<-sum(mn_chr$votes)/sum(mn_chr$county_population)
oh_turnout<-sum(oh_chr$votes)/sum(oh_chr$county_population)
wi_turnout<-sum(wi_chr$votes)/sum(wi_chr$county_population)

overview_vote_table<-data.frame(
  state=c("Illinois","Indiana","Michigan","Minnesota","Ohio","Wisconsin"),
  state_turnout=c(label_percent(accuracy=0.1)(il_turnout),label_percent(accuracy=0.1)(in_turnout),
                  label_percent(accuracy=0.1)(mi_turnout),label_percent(accuracy=0.1)(mn_turnout),
                  label_percent(accuracy=0.1)(oh_turnout),label_percent(accuracy=0.1)(wi_turnout)),
  state_proportion=c(label_percent(accuracy=0.1)(sum(il_chr$votes)/sum(chr_2024$votes)),
                     label_percent(accuracy=0.1)(sum(in_chr$votes)/sum(chr_2024$votes)),
                     label_percent(accuracy=0.1)(sum(mi_chr$votes)/sum(chr_2024$votes)),
                     label_percent(accuracy=0.1)(sum(mn_chr$votes)/sum(chr_2024$votes)),
                     label_percent(accuracy=0.1)(sum(oh_chr$votes)/sum(chr_2024$votes)),
                     label_percent(accuracy=0.1)(sum(wi_chr$votes)/sum(chr_2024$votes))))
colnames(overview_vote_table)<-c("State","Voter Turnout","Proportion of Votes")
print(overview_vote_table)


```

### Column {width="35%"}

```{r}
#| title: Proportion of Votes by County Ruralness
# utilize binning of counties by ruralness (reminder: 90-100% rural="Rural",0-20% rural="Urban",20-90% rural ="Mixed")
urban_voting<-chr_2024%>%group_by(urban)%>%summarise(votes=sum(county_population))

ggplot(data=urban_voting,aes(x=urban,y=votes))+
  geom_bar(stat="identity",fill="#8826b9")+
  labs(x="County Ruralness",y="Number of Votes")
```

### Column {width="35%"}

```{r}
#| title: Voter Turnout by Ruralness

chr_2024$urban<-factor(chr_2024$urban)
ggplot(data=chr_2024,aes(x=urban,y=voter_turnout,fill=urban))+
  geom_boxplot()+
  labs(x="County Ruralness",y="Percent Voter Turnout")+
  geom_signif(comparisons=list(c("Urban","Rural"),c("Rural","Mixed")),map_signif_level=TRUE)+
  geom_signif(comparisons=list(c("Urban","Mixed")),map_signif_level=TRUE,y_position=105)+
  ylim(0,110)+theme_bw()+
  scale_fill_manual(values=c("grey50","grey90","grey10"))
```

## Row {.tabset height="40%"}

```{r}
#| title: State Voting by Ruralness

ggplot()+
  geom_point(data=il_chr,aes(x=rural_raw,y=log10(votes),color="Illinois"))+
  geom_point(data=in_chr,aes(x=rural_raw,y=log10(votes),color="Indiana"))+
  geom_point(data=mi_chr,aes(x=rural_raw,y=log10(votes),color="Michigan"))+
  geom_point(data=mn_chr,aes(x=rural_raw,y=log10(votes),color="Minnesota"))+
  geom_point(data=oh_chr,aes(x=rural_raw,y=log10(votes),color="Ohio"))+
  geom_point(data=wi_chr,aes(x=rural_raw,y=log10(votes),color="Wisconsin"))+
  geom_smooth(data=chr_2024,aes(x=rural_raw,y=log10(votes)),method="lm",formula='y~x',color="black")+
  stat_poly_eq(data=chr_2024,aes(x=rural_raw,y=log10(votes)))+
  labs(x="Percent Rural Population",y="log10(Number of Votes)")+
  xlim(0,100)+ylim(0,10)
```

```{r}
#| title: State Voting by Gender

ggplot()+
  geom_point(data=il_chr,aes(x=female_raw,y=log10(votes),color="Illinois"))+
  geom_point(data=in_chr,aes(x=female_raw,y=log10(votes),color="Indiana"))+
  geom_point(data=mi_chr,aes(x=female_raw,y=log10(votes),color="Michigan"))+
  geom_point(data=mn_chr,aes(x=female_raw,y=log10(votes),color="Minnesota"))+
  geom_point(data=oh_chr,aes(x=female_raw,y=log10(votes),color="Ohio"))+
  geom_point(data=wi_chr,aes(x=female_raw,y=log10(votes),color="Wisconsin"))+
  geom_smooth(data=chr_2024,aes(x=female_raw,y=log10(votes)),method="lm",formula='y~x',color="black")+
  stat_poly_eq(data=chr_2024,aes(x=female_raw,y=log10(votes)))+
  labs(x="Percent Female Population",y="log10(Number of Votes)")+
  xlim(35,65)+ylim(0,10)
```

```{r}
#| title: Voter Turnout by State

chr_2024$state<-factor(chr_2024$state)
ggplot(data=chr_2024,aes(x=state,y=voter_turnout,color=state))+
  geom_boxplot()+
  labs(x="State",y="Percent Voter Turnout")+
  geom_signif(comparisons=list(c("IL","IN"),c("MI","MN"),c("OH","WI")),map_signif_level=TRUE,y_position=100)+
  geom_signif(comparisons=list(c("IN","MI"),c("MN","OH")),map_signif_level=TRUE,y_position=110)+
  geom_signif(comparisons=list(c("IL","MI"),c("MN","WI")),map_signif_level=TRUE,y_position=120)+
  geom_signif(comparisons=list(c("IN","MN")),map_signif_level=TRUE,y_position=25)+
  geom_signif(comparisons=list(c("OH","IN")),map_signif_level=TRUE,y_position=15)+
  geom_signif(comparisons=list(c("MI","OH")),map_signif_level=TRUE,y_position=130)+
  geom_signif(comparisons=list(c("MN","IL")),map_signif_level=TRUE,y_position=140)+
  geom_signif(comparisons=list(c("IN","WI")),map_signif_level=TRUE,y_position=150)+
  geom_signif(comparisons=list(c("WI","IL")),map_signif_level=TRUE,y_position=35)+
  ylim(0,155)+theme_bw()
```

# Illinois {orientation="columns"}

## Column {width="60%"}

### Row {height="20%"}

```{r}
#| content: valuebox
#| title: "Population"

list(
  #icon="clipboard2-pulse",
  color="primary",
  value=sum(il_chr$county_population)
)
```

```{r}
#| content: valuebox
#| title: "Voter Turnout"

list(
  #icon="file-medical",
  color="secondary",
  value=label_percent(accuracy=0.1)(il_turnout)
)
```

```{r}
#| content: valuebox
#| title: "Estimated Rural Voter Turnout"

list(
  #icon="clipboard2-pulse",
  color="green4",
  value=label_percent(accuracy=0.1)((sum(il_chr$rural_voters)/sum(il_chr$county_population)))
)
```

```{r}
#| content: valuebox
#| title: "Estimated Female Voter Turnout"

list(
  #icon="clipboard2-pulse",
  color="orange",
  value=label_percent(accuracy=0.1)((sum(il_chr$female_voters)/sum(il_chr$county_population)))
)
```

### Row {height="40%"}

```{r}
#| title: Voter Turnout by Ruralness

il_chr$urban<-factor(il_chr$urban)
ggplot(data=il_chr,aes(x=urban,y=voter_turnout,fill=urban))+
  geom_boxplot()+
  labs(x="County Ruralness",y="Percent Voter Turnout")+
  geom_signif(comparisons=list(c("Urban","Rural"),c("Rural","Mixed")),map_signif_level=TRUE)+
  geom_signif(comparisons=list(c("Urban","Mixed")),map_signif_level=TRUE,y_position=95)+
  ylim(0,100)+theme_bw()+
  scale_fill_manual(values=c("grey50","grey90","grey10"))
```

```{r}
#| title: Voter Turnout by Gender

#male_chr<-il_chr|>filter(gender=="Male")
#female_chr<-il_chr|>filter(gender=="Female")
#t.test(male_chr$voter_turnout,female_chr$voter_turnout)


il_chr$gender<-factor(il_chr$gender)
ggplot(data=il_chr,aes(x=gender,y=voter_turnout,fill=gender))+
  geom_boxplot()+
  labs(x="County Majority Gender",y="Voter Turnout")+
  geom_signif(comparisons=list(c("Male","Female")),map_signif_level=TRUE,y_position=105)+
  ylim(0,110)+theme_bw()+
  scale_fill_manual(values=c("hotpink1","blue"))
```

### Row {.tabset height="40%"}

```{r}
#| title: Gender and County Population

ggplot(data=il_chr,aes(x=female_raw,y=log10(county_population)))+
  geom_point(color="darkred")+
  geom_smooth(method="lm",formula=y~x)+
  stat_poly_eq()+
  labs(x="Percent Female Population",y="log10(County Population)")+
  xlim(35,65)+ylim(0,10)
```

```{r}
#| title: Gender and County Ruralness

ggplot(data=il_chr,aes(x=female_raw,y=rural_raw))+
  geom_point(color="darkblue")+
  geom_smooth(method="lm",formula=y~x)+
  stat_poly_eq()+
  labs(x="Percent Female Population",y="Percent Rural Population")+
  xlim(35,65)+ylim(0,100)
```

```{r}
#| title: County Ruralness and Population

ggplot(data=il_chr,aes(y=log10(county_population),x=rural_raw))+
  geom_point(color="darkgreen")+
  geom_smooth(method="lm",formula=y~x)+
  stat_poly_eq()+
  labs(x="Percent Rural Population",y="log10(County Population)")+
  ylim(0,10)+xlim(0,100)
```

## Column {width="40%"}

```{r}
#| title: Data

il_chr|>
  select(-state,-fipscode,-county_size,-rural_voters,-female_voters)|>
  arrange(county)|>
  datatable(
    colnames=c("Percent Female Population","Percent Voter Turnout","Population",
               "Percent Rural Population","Majority Gender","Ruralness"),
    rownames=FALSE,
    class='cell-border stripe',
    options=list(
      dom="lrtip", 
      paging=TRUE,
      lengthMenu=c(5,10,50),
      pageLength=10, 
      scrollY=TRUE
    ),
  )
```

# Indiana {orientation="columns"}

## Column {width="60%"}

### Row {height="20%"}

```{r}
#| content: valuebox
#| title: "Population"

list(
  #icon="clipboard2-pulse",
  color="primary",
  value=sum(in_chr$county_population)
)
```

```{r}
#| content: valuebox
#| title: "Voter Turnout"

list(
  #icon="file-medical",
  color="secondary",
  value=label_percent(accuracy=0.1)(in_turnout)
)
```

```{r}
#| content: valuebox
#| title: "Estimated Rural Voter Turnout"

list(
  #icon="clipboard2-pulse",
  color="green4",
  value=label_percent(accuracy=0.1)((sum(in_chr$rural_voters)/sum(in_chr$county_population)))
)
```

```{r}
#| content: valuebox
#| title: "Estimated Female Voter Turnout"

list(
  #icon="clipboard2-pulse",
  color="orange",
  value=label_percent(accuracy=0.1)((sum(in_chr$female_voters)/sum(in_chr$county_population)))
)
```

### Row {height="40%"}

```{r}
#| title: Voter Turnout by Ruralness

in_chr$urban<-factor(in_chr$urban)
ggplot(data=in_chr,aes(x=urban,y=voter_turnout,fill=urban))+
  geom_boxplot()+
  labs(x="County Ruralness",y="Percent Voter Turnout")+
  geom_signif(comparisons=list(c("Urban","Rural"),c("Rural","Mixed")),map_signif_level=TRUE)+
  geom_signif(comparisons=list(c("Urban","Mixed")),map_signif_level=TRUE,y_position=95)+
  ylim(0,100)+theme_bw()+
  scale_fill_manual(values=c("grey50","grey90","grey10"))
```

```{r}
#| title: Voter Turnout by Gender

#male_chr<-in_chr|>filter(gender=="Male")
#female_chr<-in_chr|>filter(gender=="Female")
#t.test(male_chr$voter_turnout,female_chr$voter_turnout)


in_chr$gender<-factor(in_chr$gender)
ggplot(data=in_chr,aes(x=gender,y=voter_turnout,fill=gender))+
  geom_boxplot()+
  labs(x="County Majority Gender",y="Voter Turnout")+
  geom_signif(comparisons=list(c("Male","Female")),map_signif_level=TRUE,y_position=105)+
  ylim(0,110)+theme_bw()+
  scale_fill_manual(values=c("hotpink1","blue"))
```

### Row {.tabset height="40%"}

```{r}
#| title: Gender and County Population

ggplot(data=in_chr,aes(x=female_raw,y=log10(county_population)))+
  geom_point(color="darkred")+
  geom_smooth(method="lm",formula=y~x)+
  stat_poly_eq()+
  labs(x="Percent Female Population",y="log10(County Population)")+
  xlim(35,65)+ylim(0,10)
```

```{r}
#| title: Gender and County Ruralness

ggplot(data=in_chr,aes(x=female_raw,y=rural_raw))+
  geom_point(color="darkblue")+
  geom_smooth(method="lm",formula=y~x)+
  stat_poly_eq()+
  labs(x="Percent Female Population",y="Percent Rural Population")+
  xlim(35,65)+ylim(0,100)
```

```{r}
#| title: County Ruralness and Population

ggplot(data=in_chr,aes(y=log10(county_population),x=rural_raw))+
  geom_point(color="darkgreen")+
  geom_smooth(method="lm",formula=y~x)+
  stat_poly_eq()+
  labs(x="Percent Rural Population",y="log10(County Population)")+
  ylim(0,10)+xlim(0,100)
```

## Column {width="40%"}

```{r}
#| title: Data

in_chr|>
  select(-state,-fipscode,-county_size,-rural_voters,-female_voters)|>
  arrange(county)|>
  datatable(
    colnames=c("Percent Female Population","Percent Voter Turnout","Population",
               "Percent Rural Population","Majority Gender","Ruralness"),
    rownames=FALSE,
    class='cell-border stripe',
    options=list(
      dom="lrtip", 
      paging=TRUE,
      lengthMenu=c(5,10,50),
      pageLength=10, 
      scrollY=TRUE
    ),
  )
```

# Michigan {orientation="columns"}

## Column {width="60%"}

### Row {height="20%"}

```{r}
#| content: valuebox
#| title: "Population"

list(
  #icon="clipboard2-pulse",
  color="primary",
  value=sum(mi_chr$county_population)
)
```

```{r}
#| content: valuebox
#| title: "Voter Turnout"

list(
  #icon="file-medical",
  color="secondary",
  value=label_percent(accuracy=0.1)(mi_turnout)
)
```

```{r}
#| content: valuebox
#| title: "Estimated Rural Voter Turnout"

list(
  #icon="clipboard2-pulse",
  color="green4",
  value=label_percent(accuracy=0.1)((sum(mi_chr$rural_voters)/sum(mi_chr$county_population)))
)
```

```{r}
#| content: valuebox
#| title: "Estimated Female Voter Turnout"

list(
  #icon="clipboard2-pulse",
  color="orange",
  value=label_percent(accuracy=0.1)((sum(mi_chr$female_voters)/sum(mi_chr$county_population)))
)
```

### Row {height="40%"}

```{r}
#| title: Voter Turnout by Ruralness

mi_chr$urban<-factor(mi_chr$urban)
ggplot(data=mi_chr,aes(x=urban,y=voter_turnout,fill=urban))+
  geom_boxplot()+
  labs(x="County Ruralness",y="Percent Voter Turnout")+
  geom_signif(comparisons=list(c("Urban","Rural"),c("Rural","Mixed")),map_signif_level=TRUE)+
  geom_signif(comparisons=list(c("Urban","Mixed")),map_signif_level=TRUE,y_position=95)+
  ylim(0,100)+theme_bw()+
  scale_fill_manual(values=c("grey50","grey90","grey10"))
```

```{r}
#| title: Voter Turnout by Gender

#male_chr<-mi_chr|>filter(gender=="Male")
#female_chr<-mi_chr|>filter(gender=="Female")
#t.test(male_chr$voter_turnout,female_chr$voter_turnout)


mi_chr$gender<-factor(mi_chr$gender)
ggplot(data=mi_chr,aes(x=gender,y=voter_turnout,fill=gender))+
  geom_boxplot()+
  labs(x="County Majority Gender",y="Voter Turnout")+
  geom_signif(comparisons=list(c("Male","Female")),map_signif_level=TRUE,y_position=105)+
  ylim(0,110)+theme_bw()+
  scale_fill_manual(values=c("hotpink1","blue"))
```

### Row {.tabset height="40%"}

```{r}
#| title: Gender and County Population

ggplot(data=mi_chr,aes(x=female_raw,y=log10(county_population)))+
  geom_point(color="darkred")+
  geom_smooth(method="lm",formula=y~x)+
  stat_poly_eq()+
  labs(x="Percent Female Population",y="log10(County Population)")+
  xlim(35,65)+ylim(0,10)
```

```{r}
#| title: Gender and County Ruralness

ggplot(data=mi_chr,aes(x=female_raw,y=rural_raw))+
  geom_point(color="darkblue")+
  geom_smooth(method="lm",formula=y~x)+
  stat_poly_eq()+
  labs(x="Percent Female Population",y="Percent Rural Population")+
  xlim(35,65)+ylim(0,100)
```

```{r}
#| title: County Ruralness and Population

ggplot(data=mi_chr,aes(y=log10(county_population),x=rural_raw))+
  geom_point(color="darkgreen")+
  geom_smooth(method="lm",formula=y~x)+
  stat_poly_eq()+
  labs(x="Percent Rural Population",y="log10(County Population)")+
  ylim(0,10)+xlim(0,100)
```

## Column {width="40%"}

```{r}
#| title: Data

mi_chr|>
  select(-state,-fipscode,-county_size,-rural_voters,-female_voters)|>
  arrange(county)|>
  datatable(
    colnames=c("Percent Female Population","Percent Voter Turnout","Population",
               "Percent Rural Population","Majority Gender","Ruralness"),
    rownames=FALSE,
    class='cell-border stripe',
    options=list(
      dom="lrtip", 
      paging=TRUE,
      lengthMenu=c(5,10,50),
      pageLength=10, 
      scrollY=TRUE
    ),
  )
```

# Minnesota {orientation="columns"}

## Column {width="60%"}

### Row {height="20%"}

```{r}
#| content: valuebox
#| title: "Population"

list(
  #icon="clipboard2-pulse",
  color="primary",
  value=sum(mn_chr$county_population)
)
```

```{r}
#| content: valuebox
#| title: "Voter Turnout"

list(
  #icon="file-medical",
  color="secondary",
  value=label_percent(accuracy=0.1)(mn_turnout)
)
```

```{r}
#| content: valuebox
#| title: "Estimated Rural Voter Turnout"

list(
  #icon="clipboard2-pulse",
  color="green4",
  value=label_percent(accuracy=0.1)((sum(mn_chr$rural_voters)/sum(mn_chr$county_population)))
)
```

```{r}
#| content: valuebox
#| title: "Estimated Female Voter Turnout"

list(
  #icon="clipboard2-pulse",
  color="orange",
  value=label_percent(accuracy=0.1)((sum(mn_chr$female_voters)/sum(mn_chr$county_population)))
)
```

### Row {height="40%"}

```{r}
#| title: Voter Turnout by Ruralness

mn_chr$urban<-factor(mn_chr$urban)
ggplot(data=mn_chr,aes(x=urban,y=voter_turnout,fill=urban))+
  geom_boxplot()+
  labs(x="County Ruralness",y="Percent Voter Turnout")+
  geom_signif(comparisons=list(c("Urban","Rural"),c("Rural","Mixed")),map_signif_level=TRUE)+
  geom_signif(comparisons=list(c("Urban","Mixed")),map_signif_level=TRUE,y_position=95)+
  ylim(0,100)+theme_bw()+
  scale_fill_manual(values=c("grey50","grey90","grey10"))
```

```{r}
#| title: Voter Turnout by Gender

#male_chr<-mn_chr|>filter(gender=="Male")
#female_chr<-mn_chr|>filter(gender=="Female")
#t.test(male_chr$voter_turnout,female_chr$voter_turnout)


mn_chr$gender<-factor(mn_chr$gender)
ggplot(data=mn_chr,aes(x=gender,y=voter_turnout,fill=gender))+
  geom_boxplot()+
  labs(x="County Majority Gender",y="Voter Turnout")+
  geom_signif(comparisons=list(c("Male","Female")),map_signif_level=TRUE,y_position=105)+
  ylim(0,110)+theme_bw()+
  scale_fill_manual(values=c("hotpink1","blue"))
```

### Row {.tabset height="40%"}

```{r}
#| title: Gender and County Population

ggplot(data=mn_chr,aes(x=female_raw,y=log10(county_population)))+
  geom_point(color="darkred")+
  geom_smooth(method="lm",formula=y~x)+
  stat_poly_eq()+
  labs(x="Percent Female Population",y="log10(County Population)")+
  xlim(35,65)+ylim(0,10)
```

```{r}
#| title: Gender and County Ruralness

ggplot(data=mn_chr,aes(x=female_raw,y=rural_raw))+
  geom_point(color="darkblue")+
  geom_smooth(method="lm",formula=y~x)+
  stat_poly_eq()+
  labs(x="Percent Female Population",y="Percent Rural Population")+
  xlim(35,65)+ylim(0,100)
```

```{r}
#| title: County Ruralness and Population

ggplot(data=mn_chr,aes(y=log10(county_population),x=rural_raw))+
  geom_point(color="darkgreen")+
  geom_smooth(method="lm",formula=y~x)+
  stat_poly_eq()+
  labs(x="Percent Rural Population",y="log10(County Population)")+
  ylim(0,10)+xlim(0,100)
```

## Column {width="40%"}

```{r}
#| title: Data

mn_chr|>
  select(-state,-fipscode,-county_size,-rural_voters,-female_voters)|>
  arrange(county)|>
  datatable(
    colnames=c("Percent Female Population","Percent Voter Turnout","Population",
               "Percent Rural Population","Majority Gender","Ruralness"),
    rownames=FALSE,
    class='cell-border stripe',
    options=list(
      dom="lrtip", 
      paging=TRUE,
      lengthMenu=c(5,10,50),
      pageLength=10, 
      scrollY=TRUE
    ),
  )
```

# Ohio {orientation="columns"}

## Column {width="60%"}

### Row {height="20%"}

```{r}
#| content: valuebox
#| title: "Population"

list(
  #icon="clipboard2-pulse",
  color="primary",
  value=sum(oh_chr$county_population)
)
```

```{r}
#| content: valuebox
#| title: "Voter Turnout"

list(
  #icon="file-medical",
  color="secondary",
  value=label_percent(accuracy=0.1)(oh_turnout)
)
```

```{r}
#| content: valuebox
#| title: "Estimated Rural Voter Turnout"

list(
  #icon="clipboard2-pulse",
  color="green4",
  value=label_percent(accuracy=0.1)((sum(oh_chr$rural_voters)/sum(oh_chr$county_population)))
)
```

```{r}
#| content: valuebox
#| title: "Estimated Female Voter Turnout"

list(
  #icon="clipboard2-pulse",
  color="orange",
  value=label_percent(accuracy=0.1)((sum(oh_chr$female_voters)/sum(oh_chr$county_population)))
)
```

### Row {height="40%"}

```{r}
#| title: Voter Turnout by Ruralness

oh_chr$urban<-factor(oh_chr$urban)
ggplot(data=oh_chr,aes(x=urban,y=voter_turnout,fill=urban))+
  geom_boxplot()+
  labs(x="County Ruralness",y="Percent Voter Turnout")+
  geom_signif(comparisons=list(c("Urban","Rural"),c("Rural","Mixed")),map_signif_level=TRUE)+
  geom_signif(comparisons=list(c("Urban","Mixed")),map_signif_level=TRUE,y_position=95)+
  ylim(0,100)+theme_bw()+
  scale_fill_manual(values=c("grey50","grey90","grey10"))
```

```{r}
#| title: Voter Turnout by Gender

#male_chr<-oh_chr|>filter(gender=="Male")
#female_chr<-oh_chr|>filter(gender=="Female")
#t.test(male_chr$voter_turnout,female_chr$voter_turnout)


oh_chr$gender<-factor(oh_chr$gender)
ggplot(data=oh_chr,aes(x=gender,y=voter_turnout,fill=gender))+
  geom_boxplot()+
  labs(x="County Majority Gender",y="Voter Turnout")+
  geom_signif(comparisons=list(c("Male","Female")),map_signif_level=TRUE,y_position=105)+
  ylim(0,110)+theme_bw()+
  scale_fill_manual(values=c("hotpink1","blue"))
```

### Row {.tabset height="40%"}

```{r}
#| title: Gender and County Population

ggplot(data=oh_chr,aes(x=female_raw,y=log10(county_population)))+
  geom_point(color="darkred")+
  geom_smooth(method="lm",formula=y~x)+
  stat_poly_eq()+
  labs(x="Percent Female Population",y="log10(County Population)")+
  xlim(35,65)+ylim(0,10)
```

```{r}
#| title: Gender and County Ruralness

ggplot(data=oh_chr,aes(x=female_raw,y=rural_raw))+
  geom_point(color="darkblue")+
  geom_smooth(method="lm",formula=y~x)+
  stat_poly_eq()+
  labs(x="Percent Female Population",y="Percent Rural Population")+
  xlim(35,65)+ylim(0,100)
```

```{r}
#| title: County Ruralness and Population

ggplot(data=oh_chr,aes(y=log10(county_population),x=rural_raw))+
  geom_point(color="darkgreen")+
  geom_smooth(method="lm",formula=y~x)+
  stat_poly_eq()+
  labs(x="Percent Rural Population",y="log10(County Population)")+
  ylim(0,10)+xlim(0,100)
```

## Column {width="40%"}

```{r}
#| title: Data

oh_chr|>
  select(-state,-fipscode,-county_size,-rural_voters,-female_voters)|>
  arrange(county)|>
  datatable(
    colnames=c("Percent Female Population","Percent Voter Turnout","Population",
               "Percent Rural Population","Majority Gender","Ruralness"),
    rownames=FALSE,
    class='cell-border stripe',
    options=list(
      dom="lrtip", 
      paging=TRUE,
      lengthMenu=c(5,10,50),
      pageLength=10, 
      scrollY=TRUE
    ),
  )
```

# Wisconsin {orientation="columns"}

## Column {width="60%"}

### Row {height="20%"}

```{r}
#| content: valuebox
#| title: "Population"

list(
  #icon="clipboard2-pulse",
  color="primary",
  value=sum(wi_chr$county_population)
)
```

```{r}
#| content: valuebox
#| title: "Voter Turnout"

list(
  #icon="file-medical",
  color="secondary",
  value=label_percent(accuracy=0.1)(wi_turnout)
)
```

```{r}
#| content: valuebox
#| title: "Estimated Rural Voter Turnout"

list(
  #icon="clipboard2-pulse",
  color="green4",
  value=label_percent(accuracy=0.1)((sum(wi_chr$rural_voters)/sum(wi_chr$county_population)))
)
```

```{r}
#| content: valuebox
#| title: "Estimated Female Voter Turnout"

list(
  #icon="clipboard2-pulse",
  color="orange",
  value=label_percent(accuracy=0.1)((sum(wi_chr$female_voters)/sum(wi_chr$county_population)))
)
```

### Row {height="40%"}

```{r}
#| title: Voter Turnout by Ruralness

wi_chr$urban<-factor(wi_chr$urban)
ggplot(data=wi_chr,aes(x=urban,y=voter_turnout,fill=urban))+
  geom_boxplot()+
  labs(x="County Ruralness",y="Percent Voter Turnout")+
  geom_signif(comparisons=list(c("Urban","Rural"),c("Rural","Mixed")),map_signif_level=TRUE)+
  geom_signif(comparisons=list(c("Urban","Mixed")),map_signif_level=TRUE,y_position=95)+
  ylim(0,100)+theme_bw()+
  scale_fill_manual(values=c("grey50","grey90","grey10"))
```

```{r}
#| title: Voter Turnout by Gender

#male_chr<-wi_chr|>filter(gender=="Male")
#female_chr<-wi_chr|>filter(gender=="Female")
#t.test(male_chr$voter_turnout,female_chr$voter_turnout)


in_chr$gender<-factor(in_chr$gender)
ggplot(data=wi_chr,aes(x=gender,y=voter_turnout,fill=gender))+
  geom_boxplot()+
  labs(x="County Majority Gender",y="Voter Turnout")+
  geom_signif(comparisons=list(c("Male","Female")),map_signif_level=TRUE,y_position=105)+
  ylim(0,110)+theme_bw()+
  scale_fill_manual(values=c("hotpink1","blue"))
```

### Row {.tabset height="40%"}

```{r}
#| title: Gender and County Population

ggplot(data=wi_chr,aes(x=female_raw,y=log10(county_population)))+
  geom_point(color="darkred")+
  geom_smooth(method="lm",formula=y~x)+
  stat_poly_eq()+
  labs(x="Percent Female Population",y="County Population")+
  xlim(35,65)+ylim(0,10)
```

```{r}
#| title: Gender and County Ruralness

ggplot(data=wi_chr,aes(x=female_raw,y=rural_raw))+
  geom_point(color="darkblue")+
  geom_smooth(method="lm",formula=y~x)+
  stat_poly_eq()+
  labs(x="Percent Female Population",y="Percent Rural Population")+
  xlim(35,65)+ylim(0,100)
```

```{r}
#| title: County Ruralness and Population

ggplot(data=wi_chr,aes(y=log10(county_population),x=rural_raw))+
  geom_point(color="darkgreen")+
  geom_smooth(method="lm",formula=y~x)+
  stat_poly_eq()+
  labs(x="Percent Rural Population",y="log10(County Population)")+
  ylim(0,10)+xlim(0,100)
```

## Column {width="40%"}

```{r}
#| title: Data

wi_chr|>
  select(-state,-fipscode,-county_size,-rural_voters,-female_voters)|>
  arrange(county)|>
  datatable(
    colnames=c("Percent Female Population","Percent Voter Turnout","Population",
               "Percent Rural Population","Majority Gender","Ruralness"),
    rownames=FALSE,
    class='cell-border stripe',
    options=list(
      dom="lrtip", 
      paging=TRUE,
      lengthMenu=c(5,10,50),
      pageLength=10, 
      scrollY=TRUE
    ),
  )
```

# Data

```{r all_data}
chr_2024|>
  select(-county_size,-rural_voters,-female_voters)|>
  arrange(fipscode)|>
  datatable(
    colnames=c("County Name","State","Percent Female Population","Percent Voter Turnout","Population",
               "Percent Rural Population","Majority Gender","Ruralness"),
    rownames=FALSE,
    class='cell-border stripe',
    options=list(dom='ftp',
      paging=TRUE,
      lengthMenu=c(25,50,100),
      pageLength=10, 
      scrollY=TRUE)
    )
```
